\Title

### 2021-06-28 manuscript/content.tex
Clarify the part about the A_k Jacobian matrices
Break apart the item that describes them to highlight the definition.

\noindent where $\alpha_k$ is a scalar coefficient called the \emph{step-size}
and $f$ is a function of the parameter vector $\mathbf{c}_k$.
For linear regression problems, these additive models can be written as the
matrix equation

@@

\noindent Because of the linearity of the problem, the step-size parameters
can be included into the parameter vector $\mathbf{c}_k$.

@@

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (see section \ref{sec:source_distribution} for details).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that
    fall inside the respective window.
    Since the windows overlap, the total number of sources from all sets will
    be greater than $M$.
  \item Define the vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window and matrix $\mathbf{A}_k$ as the Jacobian
    matrix between those sources and every data point of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources.
\end{enumerate}

>>>>

\noindent where $\alpha_k$ is a scalar coefficient called the \emph{step-size}
and $f$ is a function of the parameter vector $\mathbf{c}_k$.
For linear problems, these additive models can be written as the matrix
equation

@@

\noindent Because of the linearity of the $f(\mathbf{c}_k)$ functions, the
$\alpha_k$ step-size parameters can be incorporated into the parameter vector
$\mathbf{c}_k$.

@@

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (see section \ref{sec:source_distribution} for details).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that
    fall inside the respective window.
    Since the windows overlap, the total number of sources from all sets will
    be greater than $M$.
  \item Define vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window.
  \item Define matrix $\mathbf{A}_k$ as the Jacobian matrix between the sources
    in the $k$-th window and all $N$ data points of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources (i.e., Eq.~\ref{eq:gb-linear-model}).
\end{enumerate}
